Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-27 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

\footnote{\yutsung{The word ''cryptodeterminism'' is used by Peres~\cite{peres1995quantum}
without a clear definition. I tried to check its meaning from other
sources. In~\cite{Atmanspacher2014}, Atmanspacher defined 
\begin{quote}
...one might paraphrase the deterministic yet non-determinable behavior
of such systems as ``cryptodeterminism''...
\end{quote}
where ``deterministic'' and ``determinable'' is defined in the
same section as 
\begin{quote}
The recent creation of the term ``deterministic chaos'' expresses
the tension between ontic (hidden) lawfulness and epistemic (apparent)
irregularity in chaotic system. Our description of the underlying
laws of nature, e.g. by differential equations governing the dynamics
of such systems, is no doubt deterministic, but their observable behavior
is everything but determinable (in the sense of measurable, computable,
or predictable) with arbitrary precision....
\end{quote}
Is Atmanspacher's usage consistent with Peres' and ours here?}}Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

>>>>

\footnote{\yutsung{The word ''cryptodeterminism'' is used by Peres~\cite{peres1995quantum}
without a clear definition. I tried to check its meaning from other
sources.

In~\cite{PeresRon1988}, Peres and Ron defined
\begin{quote}
We now introduce the cryptodeterministic hypothesis: It is possible
to specify all the details of a preparation, so that the result of
any measurement becomes completely deterministic.
\end{quote}
Unfortunately, Google Book cannot preview all pages, and the InterLibrary
Loan hasn't finished my request, yet...

In~\cite{Atmanspacher2014}, Atmanspacher defined 
\begin{quote}
...one might paraphrase the deterministic yet non-determinable behavior
of such systems as ``cryptodeterminism''...
\end{quote}
where ``deterministic'' and ``determinable'' is defined in the
same section as 
\begin{quote}
The recent creation of the term ``deterministic chaos'' expresses
the tension between ontic (hidden) lawfulness and epistemic (apparent)
irregularity in chaotic system. Our description of the underlying
laws of nature, e.g. by differential equations governing the dynamics
of such systems, is no doubt deterministic, but their observable behavior
is everything but determinable (in the sense of measurable, computable,
or predictable) with arbitrary precision....
\end{quote}
Is Atmanspacher's usage consistent with Peres' and ours here?}}Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.
